The proof equivalence problem for multiplicative linear logic is \textsc{pspace}-complete v0.3

### 2013-09-12 main/s_background.tex
notation, some pictures, wording

\end{itemize}
%
satisfying natural coherence conditions.
%
The category $\textsc{mll}(\emptyset)$ of unit-only \MLL-formulae and equivalence classes of proofs is a $\star$-autonomous category.
%
The formulation used induces various forms of \emph{strictness}, instances where isomorphisms of the definition are identities: DeMorgan duality means $A=\dual*A$, one-sided sequents mean the closure adjunction is an equivalence of categories, and the associativities are identities by decree.
%
Modulo strictness, $\textsc{mll}(\emptyset)$ is the \emph{free} $\star$-autonomous category over the empty category $\emptyset$.
%
This means that \emph{any} $\star$-autonomous category is a model of the logic, and that \MLL\ proof equivalence is the \emph{word problem} for $\star$-autonomous categories, the problem of deciding when two representations of morphisms denote the same morphism.

@@

\begin{definition}
\label{def:proofs to nets}
%
The relation $(\toNet)$ interprets a proof by a linking $\links$ as follows:
% 
for each $\named a\bot$, if $\Gamma$ is the context of the inference introducing $\named a\bot$, as illustrated below, then $\links(a)$ is the name of some $1$ in $\Gamma$.
\[
	\infer[\MLLlabel b]{\Gamma,\named a\bot}{\Gamma}
\]
%
\end{definition}

@@

>>>>

\end{itemize}
%
satisfying natural coherence conditions.
%
%The category $\textsc{mll}(\emptyset)$ of unit-only \MLL-formulae and equivalence classes of proofs is a $\star$-autonomous category.
%
The category with as objects unit-only \MLL-formulae and as morphisms $A\to B$ the equivalence classes of proofs of $\dual A\parr B$, denoted $\textsc{mll}(\emptyset)$, is a $\star$-autonomous category.
%
The present formulation of formulae induces two forms of \emph{strictness}, instances where isomorphisms of the definition are identities: DeMorgan duality means $A=\dual*A$, while
%, one-sided sequents mean the closure adjunction is an equivalence of categories, 
associativity is an identity by decree.
%
Modulo strictness, $\textsc{mll}(\emptyset)$ is the \emph{free} $\star$-autonomous category over the empty category $\emptyset$.
%
This means that \emph{any} $\star$-autonomous category is a model of the logic, and that \MLL\ proof equivalence is the \emph{word problem} for $\star$-autonomous categories, the problem of deciding when two representations of morphisms denote the same morphism.

@@

\begin{definition}
\label{def:proofs to nets}
%
The relation $(\toNet)$ interprets a proof $\Pi$ for a sequent $\Gamma$ by a linking $\links$ as follows:
% 
$\Pi\toNet\links$ if for each $\named a\bot$ in $\Gamma$, if $\Delta$ is the context of the inference introducing $\named a\bot$, as illustrated below, then $\links(a)$ is the name of some $1$ in $\Delta$.
\[
	\infer[\MLLlabel b]{\Delta,\named a\bot}{\Delta}
\]
%
\end{definition}

@@

\subsection{Notation}

We will use a concise diagrammatic notation for sequents and proof nets.
%
The units $1$ and $\bot$ are represented by a circle $\circ$ and a disc $\bullet$ respectively.
%
A tensor is represented by a line connecting both subformulae, and a par by juxtaposition: if $A$ and $B$ are represented by \raisebox{-0.3\height}{\includegraphics[scale=0.75]{hex-A.pdf}}
and \raisebox{-0.3\height}{\includegraphics[scale=0.75]{hex-B.pdf}},
%
then $A\parr B$ is \raisebox{-0.3\height}{\includegraphics[scale=0.75]{hex-AparB.pdf}}
and $A\tn B$ is \raisebox{-0.3\height}{\includegraphics[scale=0.75]{hex-AtnB.pdf}}.
%
A tensor of multiple elements is denoted by stringing them together in a line, so $A\tn B\tn C$ is
\raisebox{-0.3\height}{\includegraphics[scale=0.75]{hex-AtnBtnC.pdf}}.
%
Boxes play the role of parentheses around par-formulae, so $(A\parr B)\tn C$ is drawn as \begin{center}{\includegraphics[scale=1]{hex-AparBtnC.pdf}}\end{center}

\noindent For example, this sequent
\[ \vdash \bot\tn\bot, \bot\tn\bot, \bot\tn\bot, \bot\tn\bot, 1, \{[(1\parr 1\parr 1)\tn(1\parr 1\parr 1)]\parr 1\parr (\bot\tn\bot\tn\bot)\parr 1\}\tn\bot \]
could be drawn like this:
\begin{center}\includegraphics[scale=0.75]{example-sequent.pdf}\end{center}

\noindent We represent a proof net by drawing an arrow from each $\bullet$ to some $\circ$. For example, one proof net on the above sequent is
\begin{center}\includegraphics[scale=0.75]{example-sequent-proofnet.pdf}\end{center}

### 2013-09-12 main/s_level_0.tex
notation, some pictures, wording

\begin{proof}
%
It will be shown by induction on the number of $\bot$-formulae in $\Gamma$ that every proof net for $\Gamma$ belongs to one of two equivalence classes.
%
For the base case, the smallest inhabited sequent with two tensor-formulae is the following.
\[
	\1,\1,\1,\bot\tn\bot,\bot\tn,\bot
\]
It has two equivalence classes of 12 proof nets each.

@@

Let $\named a\bot$ connect to $\named y\1$ in $\Delta$, and let $\named c\bot$ be a subformula of $A$, which means that for case 2, $A=\named c\bot$.
%
Then $\links'$ is obtained by adjusting $\links$ as follows.
\begin{itemize}

>>>>

\begin{figure}[p]
\[
\begin{array}{ccc}
	\basenet 1213 & \perm & \basenet 3213 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
	\basenet 1223 &		  & \basenet 3212 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
	\basenet 1323 &		  & \basenet 3112 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
	\basenet 1321 &		  & \basenet 3132 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
	\basenet 2321 &		  & \basenet 2132 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
	\basenet 2331 & \perm & \basenet 2131
\end{array}
\qquad
\begin{array}{ccc}
	\basenet 1312 & \perm & \basenet 1332 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
	\basenet 2312 &		  & \basenet 1232 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
	\basenet 2313 &		  & \basenet 1231 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
	\basenet 2113 &		  & \basenet 3231 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
	\basenet 2123 &		  & \basenet 3221 \\ \\[-6pt] \vperm && \vperm \\ \\[-6pt]
	\basenet 3123 & \perm & \basenet 3121
\end{array}
\]
\caption{The two equivalence classes of nets for $\1,\1,\1,\bot\tn\bot,\bot\tn,\bot$}
\label{fig:2x12 nets}
\end{figure}

\begin{proof}
%
It will be shown by induction on the number of $\bot$-formulae in $\Gamma$ that every proof net for $\Gamma$ belongs to one of two equivalence classes.
%
For the base case, the smallest inhabited sequent with two tensor-formulae is the following.
\[
	\1,\1,\1,\bot\tn\bot,\bot\tn,\bot
\]
It has two equivalence classes of 12 proof nets each, displayed in Figure~\ref{fig:2x12 nets}.

@@

Let $\named a\bot$ connect to $\named y\1$ in $\Delta$.
%
For case 1, let $A$ be $A'\tn\named c\bot$; for case 2, let $A=\named c\bot$.
%
Then $\links'$ is obtained by adjusting $\links$ as follows.
\begin{itemize}
